Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
added acknowledgements per journal instructions

>>>>

\section*{Acknowledgements}

Work by Daniel S.~Katz was supported by the National Science Foundation (NSF) while working at the Foundation.
Any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.
Work by Kyle E.~Niemeyer was supported in part by the NSF under grant ACI-1535065.
